### 2021-09-28 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
formatting changes

%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
\end{paracol}

@@

@@

\begin{specialtable}[H] 
    %[htbp]

@@

    \begin{tabular}{lccccccccccc}

@@

     &  & \textbf{C-LFR-ON} & & \textbf{C-CSP-ON} &  &	\textbf{C-1HTR1T-ON} &	&	&	\textbf{C-2HTR3T-ON}	&	& \\

@@

    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	N/A	&	N/A	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	N/A	&	N/A	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\

@@

    T2 Power (MW)	&	$\dot{W}_{T2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	527.8	&	485	&	485.4	\\

@@

    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	0.5484	\\

@@

    HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	34.29	&	31.61	&	31.63	\\
    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	0.8594	&	0.8074	&	0.8074	\\
    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	298.1	&	363.4	&	363.8	\\
    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	&	0.9436	&	0.9561	&	0.9561	\\
    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	N/A	&	N/A	&	71.34	&	26.92	&	33.72	&	73.4	&	35.05	&	70.88	&	44.92	&	23.13	\\
    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	N/A	&	N/A	&	0.9924	&	0.701	&	0.8104	&	0.9957	&	0.8034	&	0.9926	&	0.9138	&	0.6454	\\
    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	N/A	&	N/A	&	757.6	&	760.8	&	751.3	&	751.5	&	751.9	&	751.3	&	751.3	&	751.9	\\
    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	N/A	&	N/A	&	0.945	&	0.945	&	0.945	&	0.9381	&	0.9374	&	0.9450	&	0.9493	&	0.9493	\\

@@

The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications. Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction. Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations. Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.

@@

The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually. C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%. The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}. Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficency perspective, but reduces the LFR thermal power. This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power. In principle, dropping the LFR inlet temperature further, to as low as 340^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed. When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.   
\bl{text revised}

@@

\end{paracol}
\begin{specialtable}[H] 
    %[htbp]
    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
    \resizebox{\columnwidth}{!}{
    \begin{tabular}{lccccccc}
    \toprule
     &  & \textbf{C-LFR-PRE} & \textbf{C-LFR-PAR} &  &	\textbf{C-LFR-CIRC} &	& \\
    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
    \midrule
    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	N/A	&	N/A	&	N/A	\\
    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	N/A	&	N/A	&	N/A	\\
    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	N/A	&	N/A	&	N/A	\\
    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	N/A	&	N/A	&	N/A	&	0.7245	&	98.25	&	244.2	\\
    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	N/A	&	N/A	&	N/A	\\
    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	N/A	&	N/A	&	N/A	\\
    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	N/A	&	N/A	&	N/A	\\
    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	N/A	&	N/A	&	N/A	\\
    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	N/A	&	N/A	&	N/A	\\
    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
    \bottomrule
    \end{tabular}
    }
\end{specialtable}
\begin{paracol}{2}
\linenumbers
\switchcolumn

@@

>>>>

%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}

@@

%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
\end{paracol}

@@

The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications. Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction. Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations. Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component. 
\clearpage 
\mw{Check that the column breakdown and grouping is correct in what I've changed.}
\end{paracol}
\begin{specialtable}[H] 
    %[htbp]

@@

    \begin{tabular}{lc|cc|cc|ccc|ccc}

@@

     &  & \multicolumn{2}{c}{\textbf{C-LFR-ON}} & \multicolumn{2}{|c}{\textbf{C-CSP-ON}}  &	\multicolumn{3}{|c}{\textbf{C-1HTR1T-ON}}	&	\multicolumn{3}{|c}{\textbf{C-2HTR3T-ON}} \\

@@

    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,4C,5A}$	&	415.1	&	400	&	$\cdot$	&	$\cdot$	&	380	&	400	&	400	&	415.2	&	400	&	400	\\
    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	$\cdot$	&	$\cdot$	&	390	&	440	&	390	&	410	&	440	&	390	&	390	&	440	\\

@@

    T2 Power (MW)	&	$\dot{W}_{T2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	527.8	&	485	&	485.4	\\

@@

    LFR Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.4485	&	0.4928	&	0.4929	&	0.5478	&	0.5486	&	0.5484	\\

@@

    HTR2 UA Value (MW/$^{\circ}$C)	&	$UA_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	34.29	&	31.61	&	31.63	\\
    HTR2 Capacitance Ratio (-)	&	$CR_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.8594	&	0.8074	&	0.8074	\\
    HTR2 Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	298.1	&	363.4	&	363.8	\\
    HTR2 Effectiveness (-)	&	$\varepsilon_{HTR2}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.9436	&	0.9561	&	0.9561	\\
    CSPHX UA Value (MW/$^{\circ}$C)	&	$UA_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	71.34	&	26.92	&	33.72	&	73.4	&	35.05	&	70.88	&	44.92	&	23.13	\\
    CSPHX Capacitance Ratio (-)	&	$CR_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	0.9924	&	0.701	&	0.8104	&	0.9957	&	0.8034	&	0.9926	&	0.9138	&	0.6454	\\
    CSPHX Heat Transfer Rate (MW)	&	$\dot{Q}_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	757.6	&	760.8	&	751.3	&	751.5	&	751.9	&	751.3	&	751.3	&	751.9	\\
    CSPHX Effectiveness (-)	&	$\varepsilon_{CSPHX}$	&	$\cdot$	&	$\cdot$	&	0.945	&	0.945	&	0.945	&	0.9381	&	0.9374	&	0.9450	&	0.9493	&	0.9493	\\

@@

@@

The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually. C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%. The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}. Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficency perspective, but reduces the LFR thermal power. This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power. In principle, dropping the LFR inlet temperature further, to as low as 340$^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed. When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.   
\bl{text revised}

@@

@@

\begin{specialtable}[H]  
    %[htbp]
    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
    \resizebox{\columnwidth}{!}{
    \begin{tabular}{lc|c|cc|ccc}
    \toprule
     &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
    \midrule
    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
    \bottomrule
    \end{tabular}
    }
\end{specialtable}
% \begin{paracol}{2}
% \linenumbers
% \switchcolumn
